---
title: "Analysis of BSFG run Sept 12, 2017"
author: "Caryn Johansen"
date: "9/13/2017"
output: html_document
---

# Introduction

The purpose of this document is to analysis the posterior of the BSFG run that began on September 12, 2017.

Pathway for this data on my local computer is: `/Users/caryn/Box\ Sync/Projects/maize_BSFG/analysis/rep-12-09-2017`

Pathway for this analysis on farm, where is ran, is: `/home/caryn89/Projects/maize_BSFG/analysis/rep-12-09-2017`

This analysis should be done on the local drive. Look for a `analysis.R` file to run on Farm in order to take advantage of the full posterior.

the `current_loop.RData` data file is the BSFG_state object saved at the end of each loop. Once the run is complete, the `postrun.RData` file will be the final `BSFG_state` object.

```{r}
load("current_loop.RData")
```

Libraries for analysis:

```{r, message=FALSE}
library(reshape2)
library(BSFG)
library(tidyverse)
library(ggplot2)
```


# Local current state

Which run

```{r, results='hold', fig.show='hold'}
(BSFG_state$current_state$nrun)
(BSFG_state$current_state$total_time)
```


```{r}
lambda <- BSFG_state$current_state$Lambda
dim(lambda)
```

I want the gene names. I didn't do this run with the appropriate data set that had the gene names in it. Note for future.

```{r}
exp <- read.table("~/Box Sync/UCD/RRI/maize_genomics_project/data/eQTL/maize_414_expressedFPKM_names.txt", sep=",", header=T, row.names = 1)
genes <- colnames(exp)
rownames(lambda) <- genes
```


reshape for graphing and analysis

```{r, results='hold', fig.show='hold'}
lambda <- melt(lambda)
head(lambda)
colnames(lambda) <- c("genes", "factor", "value")
```

Range of factors

```{r}
lambda %>%
  group_by(factor) %>%
  summarise(min = min(value), max=max(value))
```

Plot the spread of the effect sizes for each gene in each factor

```{r}
lambda %>%
  ggplot() + geom_boxplot(aes(as.factor(factor), y=value))
```

# $h^2$ of factors

```{r}
h2_factors <- as.data.frame(BSFG_state$current_state$F_h2)
h2_factors <- melt(h2_factors)
h2_factors$factor <- seq(1:20)

h2_factors %>%
  ggplot() + geom_bar(aes(x=variable, y=value), stat = "identity")
```

On top of the lambda values

```{r}
lambda %>%
  ggplot() + geom_bar(data=h2_factors, aes(x=as.factor(factor), y=value), stat = "identity") + geom_boxplot(aes(as.factor(factor), y=value))
```

Confused about how heritability of factor relates to lambda. Why do factors 19 and 20 have such high heritabilities?? Maybe my data is getting switched around...

By-gene heritability

```{r}
gene_h2 <- current_state$resid_h2
gene_h2 <- melt(gene_h2)
gene_h2$Var1 <- NULL
gene_h2$gene <- genes

```


# Creating modules

Threshold for the lambda value for being in the module is |0.2|

```{r, results='hold', fig.show='hold'}
lambda %>%
  ggplot() + geom_boxplot(aes(x=as.factor(factor), y=value)) + geom_hline(yintercept = c(0.2, -0.2), color="red")
```

Create modules for the factors:

```{r, results='hold', fig.show='hold'}
modules <- lambda %>%
  filter(abs(value) >= 0.2)
dim(modules)
table(modules$factor)

gene_module_density <- as.data.frame(table(modules$genes))
gene_module_density %>%
  ggplot() + geom_histogram(aes(x=Freq))
max(gene_module_density$Freq)
min(gene_module_density$Freq)
```

How many genes are not any cluster?

```{r, results='hold', fig.show='hold'}
length(which(gene_module_density$Freq == 0))

length(which(gene_module_density$Freq > 0))

length(which(gene_module_density$Freq == 0)) + length(which(gene_module_density$Freq > 0))
```

About half of the genes analyzed are not in modules.

```{r}
modules$factor <- as.factor(modules$factor)
#saveRDS(modules, file="modules_09122017.rds")
```

File saved as an RDS on Sept 13, 2017. File location: `/Users/caryn/Box\ Sync/Projects/maize_BSFG/analysis/rep-12-09-2017`



```{r}
sessionInfo()
```

